Reducing Acceptance Marks in Emerson-Lei Automata by QBF-solving

### 2022-03-04 paper/main.tex
almost submitted for SAT 2022 (+some todo notes)

We have presented a QBF-based method that reduces the number of
acceptance marks in transition-based Emerson-Lei automata. The method
has been implemented and our experimental results show that it is possible
to use the QBF solvers to find equivalent acceptance conditions of TELA
without changes to their structure.
The reduction of acceptance marks is not the only purpose of the approach,
one could possibly look for e.g. equivalent parity automata or automata without
$\Fin$-marks, depending on the subsequent use of the automata.
Even though the QBF queries can be time-consuming, in practice it can be well
used and one can find a good trade-off between speed and efficiency by setting
a reasonable timeout.

In the future work, it could be examined how the reductions of the acceptance
condition can contribute to further reduction of the state space by enabling
various optimizations, e.g. simulations.

@@

>>>>

We have presented an application of QBF solving to reduction of the number of
acceptance marks in transition-based Emerson-Lei automata. The method
has been implemented and our experimental results show that it is possible
to use the QBF solvers to find equivalent acceptance conditions of TELA
with less acceptance marks and without changes to automata structure.

The reduction of acceptance marks is not the only application of the
presented approach: one could possibly look for, e.g., equivalent
parity automata or automata without $\Fin$-marks, depending on the
subsequent use of the automata. Even though the QBF queries can be
time-consuming, in practice it can be well used and one can find a
good trade-off between speed and efficiency by choosing precision of
the reduction and setting a reasonable timeout.

In the future work, it could be examined how the reductions of the acceptance
condition can contribute to further reduction of the state space by enabling
various optimizations, e.g., simulations.

@@

\section{TODO}

Do submission:
\begin{itemize}
\item do experimentu napsat, jaky hardware pouzivame (merit cas bez toho nedava smysl)
\item spustit experimenty bez timeoutu na telatko (?a delsi timeout na QBF?)
\item prelestit text v poslednich dvou kapitolach
\end{itemize}

\noindent
Do budoucna:
\begin{itemize}
\item level 1 bez SCC optimalizace
\item nahradit weak SCC jednou hranou pro neakceptujici a jinou pro akceptujici
\item sladit konstrukci QBF formuli s implementaci
\item podivat se znovu na uzitecnost a potrebnost optimalizaci typu ``klauzule neni false'' a ``alespon jedna klauzule je neprazdna''
\item sladit popis algoritmu s implementaci
\item v experimentech nejak sledovat vztah usetreneho casu a usetrenych znacek?
\item zkusit aplikovat na jine typy automatu (treba TGBA nebo Rabin)?
\item zkusit, zda/jak redukce znacek umozni redukovat stavovy prostor
\end{itemize}
